Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-04-13 paper-webserver.tex
ADD: spfy performance images into te

@@

Spfy is similar to these technologies in that it automates workflows for users and uses task queues to distribute selected analyses.
% re: Matt "2. When comparing to IRIDA, BAP etc., can mention some differences with Superphy, e.g. the storage of interim result data that allows downstream integrated analysis"

% If we mention speed comparisons, we need to have actual data supporting them
On a per file basis, Spfy performs at a similar speed to BAP on predictive genomics tasks, though Spfy does not provide genome assembly services.
After accounting for assembly services, BAP reported \cite{thomsen2016bacterial} an average runtime of 8-9 minutes per genome over 476 runs.
ResFinder, which is similar to the RGI program used by Spfy, took an average of 3-4 minutes.
However, unlike these workflow managers, Spfy is designed to help solve the needless re-computation of analyses by storing results in a graph database for downstream comparative studies. This allows Spfy to perform population-wide analyses, regardless of the individual software used to generate the results for a given genome.

>>>>

On analysis tasks, Spfy runs all included modules in 130 seconds on average, per file \ref{fig:spfy_performance}.
Spfy can also queue up batches of files for analysis, decreasing the average runtime to 54 seconds on average with a degree of parallelization.

\begin{figure}[!htb]
\minipage{0.5\textwidth}
  \includegraphics[width=\linewidth]{images/spfy_indivs.png}
\endminipage\hfill
\minipage{0.5\textwidth}%
  \includegraphics[width=\linewidth]{images/spfy_batches.png}
\endminipage
\caption{Runtimes of Spfy's analysis modules. Left: 100 genome files are ran one-by-one with different colors representing the runtimes of the analysis module; Blue indicates the total runtime and the line represents the average runtime per file. Right: batches of files are run of increasing size. As indicated by the line, the average runtime per genome in consistant when running more than one file. This is due to the degree of parallelization meeting the capacity of the host computer.}\label{fig:spfy_performance}
\end{figure}

@@

Spfy is similar to these technologies in that it automates workflows for users and uses task queues to distribute selected analyses.
% re: Matt "2. When comparing to IRIDA, BAP etc., can mention some differences with Superphy, e.g. the storage of interim result data that allows downstream integrated analysis"
% If we mention speed comparisons, we need to have actual data supporting them
On a per file basis, Spfy performs at a similar speed to BAP on predictive genomics tasks, though Spfy does not provide genome assembly services.
After accounting for assembly services, BAP reported \cite{thomsen2016bacterial} an average runtime of 8-9 minutes per genome over 476 runs which is in the same scale as Spfy's average of over 2 minutes.
ResFinder, which is similar to the RGI program used by Spfy, took an average of 3-4 minutes whereas RGI took an average of 1 minute 30 seconds.

However, unlike these workflow managers, Spfy is designed to help solve the needless re-computation of analyses by storing results in a graph database for downstream comparative studies \ref{db_comparison}. This allows Spfy to perform population-wide analyses, regardless of the individual software used to generate the results for a given genome.
